A new machine-learning-based prediction of survival in patients with end-stage liver disease

### 2022-08-09 analysis/article.Rmd
fix: add dash between machine-learning

---
# R markdown template taken from
# Dan Holmes <dtholmes@mail.ubc.ca>
# https://labrtorian.com/2019/08/26/rmarkdown-template-that-manages-academic-affiliations/
title: "A new machine-learning based prediction of survival in patients with end-stage liver disease"
subtitle: >
    Comparision against MELD, MELD-Na, MELD-Plus7.
abstract: >
  **Objectives**:
      The shortage of grafts for liver transplantation requires
      risk stratification and adequate allocation rules.
      This study aims to improve the model of end-stage liver disease (MELD)
      score for 90-day mortality prediction with the help of different
      machine-learning algorithms.

@@

  **Keywords**:
      end-stage liver disease; IL-6; machine learning; MELD;
      risk stratification; survival estimation

>>>>

---
# R markdown template taken from
# Dan Holmes <dtholmes@mail.ubc.ca>
# https://labrtorian.com/2019/08/26/rmarkdown-template-that-manages-academic-affiliations/
title: "A new machine-learning-based prediction of survival in patients with end-stage liver disease"
subtitle: >
    Comparision against MELD, MELD-Na, MELD-Plus7.
abstract: >
  **Objectives**:
      The shortage of grafts for liver transplantation requires
      risk stratification and adequate allocation rules.
      This study aims to improve the model of end-stage liver disease (MELD)
      score for 90-day mortality prediction with the help of different
      machine-learning algorithms.

@@

  **Keywords**:
      end-stage liver disease; IL-6; machine-learning; MELD;
      risk stratification; survival estimation

### 2022-08-09 analysis/supplement.Rmd
fix: add dash between machine-learning

---
title: "A new model to predict survival in patients with end-stage liver disease"
subtitle: >
    Supplement
author:
    - Sebastian Gibb^[mail@sebastiangibb.de]
    - Thomas Berg
    - Daniel Seehofer
    - Berend Isermann
    - Thorsten Kaiser
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
output:
  bookdown::html_document2:
    toc: false
  bookdown::word_document2:
    keep_md: true
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --csl=pandoc/csl/vancouver.csl
---

>>>>

---
title: "A new machine-learning-based prediction of survival in patients with end-stage liver disease"
subtitle: >
    Supplement
author:
    - Sebastian Gibb^[mail@sebastiangibb.de]
    - Thomas Berg
    - Adam Herber
    - Daniel Seehofer
    - Berend Isermann
    - Thorsten Kaiser
bibliography:
  - "`r rprojroot::find_rstudio_root_file('analysis', 'bibliography', 'bibliography.bib')`"
output:
  bookdown::html_document2:
    toc: false
  bookdown::word_document2:
    keep_md: true
    pandoc_args: # pandoc_args doesn't support r evaluation
      - --csl=pandoc/csl/vancouver.csl
---
